The \dealii{} Library, Version 9.4

### 2022-06-24 9.4/paper.tex
add short announcement and mention step-81 in paper

The major changes of this release are:
%
\begin{itemize}
  \item Advances in simplex- and mixed-mesh support (see Section~\ref{sec:simplex});
  \item Repartitioning of distributed meshes (see Section~\ref{sec:repartitioning});
  \item Advances in matrix-free infrastructure (see Section~\ref{sec:mf});
  \item Advances in multigrid infrastructure (see Section~\ref{sec:multigrid});
  \item CutFEM support (see Section~\ref{sec:cut});
  \item Experimental integration of the Computational Geometry Algorithms Library (CGAL) (see Section~\ref{sec:cgalwrappers});
  \item Performance improvements in the particle infrastructure (see Section~\ref{sec:particles});
  \item Improvements to unstructured communication (see Section~\ref{sec:CA});
  \item Two new tutorial programs and one new code gallery program (see
    Section~\ref{subsec:steps}).
\end{itemize}
%

@@

Many of the \dealii{} tutorial programs were revised in a variety of
ways as part of this release. In addition, there are a number of new tutorial programs:
\begin{itemize}
\item \texttt{step-82} was contributed by Andrea Bonito (Texas A\&M University) and Diane Guignard (University of Ottawa). It shows how
\dealii{} can be used to implement the
local discontinuous Galerkin (LDG) method for approximating the
solution to the bi-Laplacian problem. The method is an alternative to
the C0IP method used in \texttt{step-47}.

\item \texttt{step-85} was contributed by Simon Sticko (Uppsala University). It shows how to use the new CutFEM infrastructure to solve a Poisson
problem on a circular domain that is embedded in a Cartesian background mesh.
\end{itemize}

>>>>

The major changes of this release are:
%
\begin{itemize}
  \item Advances in simplex- and mixed-mesh support (see Section~\ref{sec:simplex});
  \item Repartitioning of distributed meshes (see Section~\ref{sec:repartitioning});
  \item Advances in matrix-free infrastructure (see Section~\ref{sec:mf});
  \item Advances in multigrid infrastructure (see Section~\ref{sec:multigrid});
  \item CutFEM support (see Section~\ref{sec:cut});
  \item Experimental integration of the Computational Geometry Algorithms Library (CGAL) (see Section~\ref{sec:cgalwrappers});
  \item Performance improvements in the particle infrastructure (see Section~\ref{sec:particles});
  \item Improvements to unstructured communication (see Section~\ref{sec:CA});
  \item Three new tutorial programs and one new code gallery program (see Section~\ref{subsec:steps}).
\end{itemize}
%

@@

Many of the \dealii{} tutorial programs were revised in a variety of ways
as part of this release. In addition, there are a number of new tutorial
programs:
\begin{itemize}
  \item
    \texttt{step-81} was contributed by Manaswinee Bezbaruah (Texas A\&M
    University) and Matthias Maier (Texas A\&M University). It explains how
    to solve the complex-valued time-harmonic Maxwell's equations for an
    optical scattering problem.
  \item
    \texttt{step-82} was contributed by Andrea Bonito (Texas A\&M
    University) and Diane Guignard (University of Ottawa). It shows how
    \dealii{} can be used to implement the local discontinuous Galerkin
    (LDG) method for approximating the solution to the bi-Laplacian
    problem. The method is an alternative to the C0IP method used in
    \texttt{step-47}.
  \item
    \texttt{step-85} was contributed by Simon Sticko (Uppsala University).
    It shows how to use the new CutFEM infrastructure to solve a Poisson
    problem on a circular domain that is embedded in a Cartesian background
    mesh.
\end{itemize}
